Migration of Gas Giant Planets in Gravitationally Unstable Disks

### 2011-05-16 Text/migration.tex
Minor tweaks regarding the periodogram for the GI-active run.
	modified:   Text/migration.tex

git-svn-id: http://jaga.astro.indiana.edu/paperrepo/ApJL/Migration2010@77 3b7f7548-5c66-0410-83ab-3997167635fc

%Scott: Even more work is needed to verify (or refute) what is said here. Some of what I wrote is pure speculation and needs to be checked.
{\it The $t = 10$ Planet Run.} {\bf See note in Latex file.} The motion of the planet in this case is more difficult to interpret. We see intervals of fairly rapid inward or outward migration over several orbits, as well as times when radial migration appears to stall. Between $t = 15$ and 19 ORP, the pattern of outward migration for 2 ORP followed by an inward plunge over the next 2 ORP resembles the behavior in the $t = 0$ planet run during the burst, but, in this case, there is no distinct transition between phases of GI activity. Animations of the simulation (available at {\bf BLAH}) show there is a complex interaction between the planet, its spiral wake, and the global spiral arms caused by the instabilities. Analysis of images and periodicities suggests that, between 15 and 19 ORP, the planet may be locked in a resonance with an arm of a $m = 2$ or 3 pattern both of which have CR at 27 AU. Over this time interval the average orbit period of the planet is 0.5 ORP, while both the $m = 2$ and 3 patterns have a pattern period of $\sim 0.74$ ORP, suggesting a 2:3 resonance. It is possible that the planet actually stimulated one or both of these modes, in manner similar to what occurred in the $t = 0$ planet run, because this $m =$ ??? periodicity is absent over a similar time interval in the fiducial run.

>>>>

%Scott: Even more work is needed to verify (or refute) what is said here. Some of what I wrote is pure speculation and needs to be checked.
{\it The $t = 10$ Planet Run.} {\bf See note in Latex file.} The motion of the planet in this case is more difficult to interpret. We see intervals of fairly rapid inward or outward migration over several orbits, as well as times when radial migration appears to stall. Between $t = 15$ and 19 ORP, the pattern of outward migration for 2 ORP followed by an inward plunge over the next 2 ORP resembles the behavior in the $t = 0$ planet run during the burst, but, in this case, there is no distinct transition between phases of GI activity. Animations of the simulation (available at {\bf BLAH}) show there is a complex interaction between the planet, its spiral wake, and the global spiral arms caused by the instabilities. Analysis of images and periodicities suggests that, between 15 and 19 ORP, the planet may be locked in a resonance with an arm of a $m = 2$ or 3 pattern both of which have CR at 27 AU. Over this time interval the average orbit period of the planet is 0.5 ORP, while both the $m = 2$ and 3 patterns have a pattern period of $\sim 0.74$ ORP, suggesting a 2:3 resonance. Both of these modes are present, at nearly the same periodicities, in the fiducial run so it is possible that the planet is migrating into a resonance orbit.
